---
title: "Scraping Booking.com"
author: "Davit Mtchedluri"
date: "5/25/2020"
output:
  html_document:
    toc: yes
    toc_float: True
    number_sections: True
---
# Scraping Booking.com

##Libraries
```{r warning=FALSE}
library(robotstxt)
library(stringr)
library(rvest)
library(dplyr)

```


##Allowed or Not
checking if scraping booking.com is allowed
```{r}
paths_allowed('https://www.booking.com/')
```


defining URL
```{r}
url_booking=("https://www.booking.com/searchresults.html?label=gen173nr-1DCAEoggI46AdIM1gEaFKIAQGYATG4ARfIAQzYAQPoAQH4AQKIAgGoAgO4Atzjm_YFwAIB&sid=3501e222cd28d5cae07e2e64ce96c956&sb=1&src=searchresults&src_elem=sb&error_url=https%3A%2F%2Fwww.booking.com%2Fsearchresults.html%3Flabel%3Dgen173nr-1DCAEoggI46AdIM1gEaFKIAQGYATG4ARfIAQzYAQPoAQH4AQKIAgGoAgO4Atzjm_YFwAIB%3Bsid%3D3501e222cd28d5cae07e2e64ce96c956%3Btmpl%3Dsearchresults%3Bcheckin_month%3D8%3Bcheckin_monthday%3D24%3Bcheckin_year%3D2020%3Bcheckout_month%3D8%3Bcheckout_monthday%3D31%3Bcheckout_year%3D2020%3Bcity%3D900047975%3Bclass_interval%3D1%3Bdest_id%3D900047975%3Bdest_type%3Dcity%3Bdtdisc%3D0%3Bfrom_sf%3D1%3Bgroup_adults%3D1%3Bgroup_children%3D0%3Binac%3D0%3Bindex_postcard%3D0%3Blabel_click%3Dundef%3Bno_rooms%3D1%3Boffset%3D0%3Bpostcard%3D0%3Broom1%3DA%3Bsb_price_type%3Dtotal%3Bshw_aparth%3D1%3Bslp_r_match%3D0%3Bsrc%3Dsearchresults%3Bsrc_elem%3Dsb%3Bsrpvid%3D846896e959990084%3Bss%3DTbilisi%3Bss_all%3D0%3Bssb%3Dempty%3Bsshis%3D0%3Bssne%3DTbilisi%3Bssne_untouched%3DTbilisi%3Btop_ufis%3D1%26%3B&ss=Tbilisi&is_ski_area=0&ssne=Tbilisi&ssne_untouched=Tbilisi&city=900047975&checkin_year=2020&checkin_month=8&checkin_monthday=24&checkout_year=2020&checkout_month=8&checkout_monthday=31&group_adults=2&group_children=0&no_rooms=1&from_sf=1")
```
```{r}
response_booking=read_html(url_booking)
```

##Separate functions
While scraping I discovered that some elements exist in every obs & some does not
At first i tried simple html_text but it only returns the existent elements and that would made data frame making complecated(at least thats what i think:d)
So I came up with the idea of scraping whole nodes(this way i have all 25 obs..on every page 25 hotels are presented) and than extracting specific pattern
Eventually I get strings which I need and empty rows..overall 25 rows per variable for each page


Hotel names
```{r}
hotel=html_nodes(response_booking,css='span.sr-hotel__name')%>%html_text(trim=T)
hotel
```


Price
```{r}
price=unlist(html_nodes(response_booking,css="div.bui-price-display__value.prco-text-nowrap-helper.prco-inline-block-maker-helper")%>%html_text(trim=T))
price
```

```{r}
distance_from_center=html_nodes(response_booking,css="div.sr_card_address_line")%>%html_text(trim = T)
distance_from_center_true=str_remove(str_remove(gsub("^.*?map","",str_remove_all(distance_from_center,'\n')),'Metro access'),'Subway Access')
distance_from_center_true

```


Coordinates
```{r}
coordinates=html_nodes(response_booking,css="div.sr_card_address_line>a")%>%html_attr('data-coords')
coordinates
```


url for each hotel
```{r}
url_to_property=paste0('https://www.booking.com/',str_remove(html_nodes(response_booking,css="h3>a")%>%html_attr('href'),'\n/'))
glimpse(url_to_property)

```


Thumbs up

```{r }
thumbs_up_html=html_nodes(response_booking,css = 'div.sr-hotel__title-wrap>span')
thumbs_up_html
thumbs_up_true=str_replace(str_replace(str_detect(html_nodes(response_booking,css = 'div.sr-hotel__title-wrap>span'),'thumbs_up'),pattern = "TRUE",replacement = "Yes"),pattern = "FALSE",replacement = "No")
```

```{r}
thumbs_up_true
```


Stars
```{r}
true_stars=str_extract(html_nodes(response_booking,css = 'div.sr-hotel__title-wrap>span'), '[0-9]-star hotel')
true_stars

```


Breakfast/Free Cancellation/Prepayment

They were under one node, so I extracted the nodes
In some cases I tried to check nodes by pattern, for example if I got list of nodes I checked for pattern "Breakfast included";the ouput is the list of TRUE and FALSE; than using str_replace i match for true and false and replace them in this case if true with 'inlcuded' and if false - 'not included'

Nodes 
```{r}
stuff=html_nodes(response_booking,css = 'div.roomPrice.roomPrice_flex.sr_discount')
str_detect(stuff, 'FREE cancellation')#check for pattern
str_detect(stuff, 'Breakfast included')
str_detect(stuff, 'No prepayment needed')
```

free cancellation
```{r}
free_cancellation=str_replace(str_replace(str_detect(html_nodes(response_booking,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'FREE cancellation'), pattern = 'TRUE', replacement = 'FREE cancellation'),pattern = 'FALSE', replacement = 'No')
free_cancellation
```


Breakfast
```{r}
breakfast=str_replace(str_replace(str_detect(html_nodes(response_booking,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'Breakfast included'), pattern = 'TRUE', replacement = 'included'),pattern = 'FALSE', replacement = 'Not inlcuded')
breakfast
```

Prepayment
```{r}
No_prepayment_needed=str_replace(str_replace(str_detect(html_nodes(response_booking,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'No prepayment needed'), pattern = 'TRUE', replacement = 'No prepayment needed'),pattern = 'FALSE', replacement = 'Prepayment needed')

No_prepayment_needed

```


Ratings
```{r}
rating_stuff=html_nodes(response_booking, css = 'div.reviewFloater')
rating_stuff_text=html_text(rating_stuff,trim = T)
rating_stuff_text
```


Number of reviews
In this case I used str_detect, because of that hotel with no reviews get NA
So I extract everything between pattern 'score__text' and '</div>'<--this is where number of reviews is placed
```{r}
true_num_reviews=str_extract(gsub(".*score__text *(.*?) *</div>.*", "\\1", html_nodes(response_booking, css = 'div.reviewFloater')), '[0-9]+ reviews')
true_num_reviews
```


Review
In this one I extract words between the score of '[0-9]' indicates on that, '(.*?)' means everything and '[0-9]+ reviews.' is the pattern with which matching should end.
```{r}
kind_words=gsub(".*[0-9] *(.*?) *[0-9]+ reviews.*", "\\1",html_nodes(response_booking, css = 'div.reviewFloater')%>%html_text(trim = T))
kind_words
```


Rating scores
in this one again with gsub i extract the scores, unfortunetely they come with extra word 'Just'..And I remoce it with str_remove
```{r}
rating_true=str_remove(gsub( " .*$", "", html_nodes(response_booking, css = 'div.reviewFloater')%>%html_text(trim = T) ), 'Just')
rating_true
```


##Here goes the scraping Function
Its just combination of the values, extracting specific info, plus bottom two new lines binding all lists as one list and after creating data frame from it 
```{r}
booking_com_function=function(url_booking){
  response_booking=read_html(url_booking)
  price=unlist(html_nodes(url_test,css="div.bui-price-display__value.prco-text-nowrap-helper.prco-inline-block-maker-helper")%>%html_text(trim=T))
  hotel=unlist(html_nodes(url_test,css='span.sr-hotel__name')%>%html_text(trim=T))
  url_to_property=unlist(paste0('https://www.booking.com/',str_remove(html_nodes(url_test,css="h3>a")%>%html_attr('href'),'\n/')))
  distance_from_center_true=unlist(str_remove(gsub("^.*?map","",str_remove_all(html_nodes(url_test,css="div.sr_card_address_line")%>%html_text(trim = T),'\n')),'Metro access'))
  coordinates=unlist(html_nodes(url_test,css="div.sr_card_address_line>a")%>%html_attr('data-coords'))
  free_cancellation=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'FREE cancellation'), pattern = 'TRUE', replacement = 'FREE cancellation'),pattern = 'FALSE', replacement = 'No'))
  breakfast=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'Breakfast included'), pattern = 'TRUE', replacement = 'included'),pattern = 'FALSE', replacement = 'Not inlcuded'))
  No_prepayment_needed=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'No prepayment needed'), pattern = 'TRUE', replacement = 'No prepayment needed'),pattern = 'FALSE', replacement = 'Prepayment needed'))
  true_stars=unlist(str_extract(html_nodes(url_test,css = 'div.sr-hotel__title-wrap>span'), '[0-9]-star hotel'))
  true_num_reviews=unlist(str_extract(gsub(".*score__text *(.*?) *</div>.*", "\\1", html_nodes(url_test, css = 'div.reviewFloater')), '[0-9]+ reviews'))
  kind_words=unlist(gsub(".*[0-9] *(.*?) *[0-9]+ reviews.*", "\\1",html_nodes(url_test, css = 'div.reviewFloater')%>%html_text(trim = T)))
  rating_true=unlist(str_remove(gsub( " .*$", "", html_nodes(url_test, css = 'div.reviewFloater')%>%html_text(trim = T) ), 'Just'))
  thumbs_up_true=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.sr-hotel__title-wrap>span'),'thumbs_up'),pattern = "TRUE",replacement = "Yes"),pattern = "FALSE",replacement = "No"))
  output=list(Hotel=hotel, hyperlink=url_to_property,Price=price ,Free_Cancellation=free_cancellation,Breakfast=breakfast,Prepayment=No_prepayment_needed, Distance_from_centre=distance_from_center_true, Coordinates=coordinates,Stars=true_stars,Number_of_reviews=true_num_reviews,Review=kind_words,Rating=rating_true,Thumbs_up=thumbs_up_true)
  return(data.frame(output))
}
```



Creating NULL 'data' object, where all scraped values will accumulate 
```{r}
data=NULL
```


##Scraping booking.com

this is for loop for scraping all pages
bottom two lines combine data from current link and existed data together
next line difines next session by going on next page
I got wierd error for price, free cancellation,prepayment, breakfast and stars..They could not extract infromation from session
Because of that I added several lines which extract link from session and defines it by resp_test=read_html(link) and no read_html(sessioin)..
Surprisingly it worked only ones:D
The error was that some values had more rows than others; for examples price would have 27 values and hotel name 25:/.. couldnot figure out why and how
So I replaced all 'response_booking' with 'url_test'(I tried bunched of stuff before) and i switched places between price and hotel
Now price goes first and hotel second
I do not know which of these changes really helped..It works and im happy

Another aspect..in search I had destination-Tbilisi for 2 adults, from August/24/2020 till August/31/2020
Even though I wrote the function, ended up not using it.. I was making alot of changes in code and working whis way was more comfortable
In conclusion, Im sure there must be a smarter and shorter way of scraping this webpage, I just dont have enough knowledge for it.



```{r warning=FALSE}
session=html_session("https://www.booking.com/searchresults.html?aid=304142&label=gen173nr-1DCAEoggI46AdIM1gEaFKIAQGYATG4ARfIAQzYAQPoAQH4AQKIAgGoAgO4Atzjm_YFwAIB&sid=3501e222cd28d5cae07e2e64ce96c956&tmpl=searchresults&checkin_month=8&checkin_monthday=24&checkin_year=2020&checkout_month=8&checkout_monthday=31&checkout_year=2020&city=900047975&class_interval=1&dest_id=900047975&dest_type=city&dtdisc=0&from_sf=1&group_adults=2&group_children=0&inac=0&index_postcard=0&label_click=undef&no_rooms=1&postcard=0&raw_dest_type=city&room1=A%2CA&sb_price_type=total&shw_aparth=1&slp_r_match=0&src=searchresults&src_elem=sb&srpvid=a5d93c9c25570019&ss=Tbilisi&ss_all=0&ssb=empty&sshis=0&ssne=Tbilisi&ssne_untouched=Tbilisi&top_ufis=1&rows=25")




data=NULL




for (i in 1:39){
  response_booking=read_html(session)
  url_test=read_html(gsub(".*Host: *(.*?) *<NA>.*", "\\1", session$handle)[2])
  price=unlist(html_nodes(url_test,css="div.bui-price-display__value.prco-text-nowrap-helper.prco-inline-block-maker-helper")%>%html_text(trim=T))
  hotel=unlist(html_nodes(url_test,css='span.sr-hotel__name')%>%html_text(trim=T))
  url_to_property=unlist(paste0('https://www.booking.com/',str_remove(html_nodes(url_test,css="h3>a")%>%html_attr('href'),'\n/')))
  distance_from_center_true=unlist(str_remove(gsub("^.*?map","",str_remove_all(html_nodes(url_test,css="div.sr_card_address_line")%>%html_text(trim = T),'\n')),'Metro access'))
  coordinates=unlist(html_nodes(url_test,css="div.sr_card_address_line>a")%>%html_attr('data-coords'))
  free_cancellation=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'FREE cancellation'), pattern = 'TRUE', replacement = 'FREE cancellation'),pattern = 'FALSE', replacement = 'No'))
  breakfast=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'Breakfast included'), pattern = 'TRUE', replacement = 'included'),pattern = 'FALSE', replacement = 'Not inlcuded'))
  No_prepayment_needed=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.roomPrice.roomPrice_flex.sr_discount'), 'No prepayment needed'), pattern = 'TRUE', replacement = 'No prepayment needed'),pattern = 'FALSE', replacement = 'Prepayment needed'))
  true_stars=unlist(str_extract(html_nodes(url_test,css = 'div.sr-hotel__title-wrap>span'), '[0-9]-star hotel'))
  true_num_reviews=unlist(str_extract(gsub(".*score__text *(.*?) *</div>.*", "\\1", html_nodes(url_test, css = 'div.reviewFloater')), '[0-9]+ reviews'))
  kind_words=unlist(gsub(".*[0-9] *(.*?) *[0-9]+ reviews.*", "\\1",html_nodes(url_test, css = 'div.reviewFloater')%>%html_text(trim = T)))
  rating_true=unlist(str_remove(gsub( " .*$", "", html_nodes(url_test, css = 'div.reviewFloater')%>%html_text(trim = T) ), 'Just'))
  thumbs_up_true=unlist(str_replace(str_replace(str_detect(html_nodes(url_test,css = 'div.sr-hotel__title-wrap>span'),'thumbs_up'),pattern = "TRUE",replacement = "Yes"),pattern = "FALSE",replacement = "No"))
  output=list(Hotel=hotel, hyperlink=url_to_property,Price=price ,Free_Cancellation=free_cancellation,Breakfast=breakfast,Prepayment=No_prepayment_needed, Distance_from_centre=distance_from_center_true, Coordinates=coordinates,Stars=true_stars,Number_of_reviews=true_num_reviews,Review=kind_words,Rating=rating_true,Thumbs_up=thumbs_up_true)
  data=data.frame(output)%>%rbind(data)
  session=follow_link(session,css='li.bui-pagination__item.bui-pagination__next-arrow>a')
  Sys.sleep(3)
}

```



```{r}
glimpse(data)
```

























